Space Matters: extending sensitivity analysis to initial spatial conditions in geosimulation models

### 2018-09-19 Response_to_Reviewers.tex

	% In the Schelling and sugarscape models how are the initial population of agents distributed? Is it random? I ask as this is unclear in the current version of the paper but it is vital if your purpose is to explore how the initial spatial configuration impacts the results of the model. Should the agents not be all located at the same location for each run to rule out the impact of initial placement of agents on the resulting patterns? This is something that is not addressed in the paper. I know for example, the Schelling model in NetLogo normally places the agents at random locations but in your reimplementation how is this done? The same goes for the sugarscape model in NetLogo. I believe a clearer description of the model initialization would be good and how its not the initial random placement of agents but the actual environment that impacts the outcomes. Maybe this was explained in the paper but I missed it.  
	\item Yes, classically, the initial distribution of agents is random in both models and, most importantly for our point, it follows a uniform distribution of density. In our implementation, the initial location of agents is also random in Schelling, but it follows a distribution of density given by the generated grid. In Sugarscape, the agents are initialised at random but the resources follow a distribution of density given by the generated grid. We have clarified this point in section 2.3
    %\comment[JR]{on regarde des indicateurs aggreges qui ne dependent pas de la trajectoire de chaque agent, si le placement initial est random il na aucune influence sur ceux-ci (cf les distribs) -> ajouter des graphes de comportement stat des modeles en Appendix ?}
	%\comment[CC]{à modifier dans le papier section 2.3}[(cc) done]

	% In Section 1.2 talk about “(monocentric vs. polycentric for example)” but in the results you don’t discuss the monocentric versions explicitly using these terms.
	\item We believe that the monocentric versions are explicitly analysed in table 1: the term "monocentric" itself does not appear in the regression results but it is only because it is taken as the reference case under the term "compact' in the regression. We have clarified this in section 3.2.
    %\comment[CC]{à modifier dans le papier section 3.2}[(cc) done]

@@

	% Rigorous experimental method described. In the matching of European metropolitan areas to your generated outputs, I wonder what you are missing by not using cities from other continents. i.e. by widening the cities available to your study it may be possible to even better discover real-world examples of your archtypes (compact, polycentric, discontinuous).
	\item \comment[JR]{to the best of my knowledge there is no full-world morphological classification of cities (and surely because global 1km density dataset is not robust enough for that - already with the European grid it is not perfect)}[(MLT) Peut-être qu'on peut intégrer sa remarque dans la partie discussion? Je ne connais pas non plus de classification morphologique des villes à l'échelle du monde. Les cas européens sont privilégiés du fait de la disponibilité de données comme Corine Land Cover et Urban Atlas (pour l'usage du sol) ou Geostat (grilles de densité de pop de résolution 1km), mais ça doit aussi exister pour les US au moins? Il y a aussi le projet gridded population of the world de l'université de Columbia mais la résolution n'est pas assez fine (2.5 arcminute) pour une analyse de la morpho urbaine.]

	% Why do you not have the same amount of repetitions for your Sugarscape (50 repetitions) and Schelling (100 repetitions) model runs?
	\item \comment[JR]{no justification for the difference in number of runs (just experimental setup contingence\ldots ) $\rightarrow$ either new runs or redo computations with 50 for Schelling}\comment[JR]{ca va etre chaud patate pour les new computations ; je vais regarder les ratio de sharpe, avec un peu de chance il y a besoin de plus de repets pour schelling...}

	% You say your models are open source - do you give details of that source?  
	\item Concerning the source code of the models, an open public repository was put into place and the link provided in the paper (to an anonymized version to ensure blind review). Similarly, the large simulation datasets used for results presented in the paper are openly available on a dataverse repository (provisorily anonymized also).
	\comment[JR]{TODO dataverse. / statement open code and data}
